---
title       : My app presentation
subtitle    : Random number exploratory statistics
author      : Dean
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- 
  
    
## Newcomers to statistics often get confused between the descriptive terms used to summarise and explain sets of values.

---

### This app will produce a user defined amount of random numbers, plot their values and give numeric definitions of the:  
  
### 1. Mean  
### 2. Median  
### 3. Lower interquartile  
### 4. Upper interquartile  
### 5. Interquartile range  
### 6. Standard deviation  

---

### Example:  

### If 100 random values are generated with a mean of ~10 and a standard deviation of ~2 Then the following outputs could be displayed  

```{r echo=FALSE}
values <- rnorm(100, 10, 2)
paste("Mean =", round(mean(values),2))
paste("Median =", round(median(values),2))
paste("Lower quartile value =", round(quantile(values, .25),2))
paste("Upper quartile value =", round(quantile(values, .75),2))
paste("Interquartile range =", round(IQR(values),2))
paste("Standard deviation =", round(sd(values),2))
```

---

### The accompanying plot will also show the values marked as vertical lines

```{r echo=FALSE, warning=FALSE}
require(ggplot2)
values <- rnorm(100, 10, 2)
vals <- data.frame(values)

  ggplot(vals, aes(x=values)) + 
        geom_histogram(binwidth= 0.5, colour="black", fill="white") +
           geom_vline(aes(xintercept=mean(values, na.rm=T)),
                     colour="red", linetype="dashed", size=1) +
         geom_vline(aes(xintercept=median(values, na.rm=T)),
                   colour="blue", linetype="dashed", size=1) +
         geom_vline(aes(xintercept= quantile(values, .25)),
                   colour="green", linetype="dashed", size=1) +
         geom_vline(aes(xintercept=quantile(values, .75)),
                   colour="green", linetype="dashed", size=1) 
```
